An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-03-31 poly-embed-journal/poly-embed-journal.tex
Thinking about nonredundancy

Several consistent convex surrogates in the literature can be thought of as ``embeddings'', wherein one maps the discrete reports to a vector space, and finds a convex loss which agrees with the original loss.
A key condition is that the original reports should be optimal exactly when the corresponding embedded points are optimal.
We formalize this notion as follows.
%
\begin{definition}[Embedding a loss]\label{def:loss-embed}
  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ if there exists some injective embedding $\varphi:\R\to\reals^d$ such that
  (i) for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\R$ we have
  % \begin{equation}\label{eq:embed-loss}
  %   r \in \argmin_{r'\in\R} \inprod{p}{\ell(r')} \iff \varphi(r) \in \argmin_{u\in\reals^d} \inprod{p}{L(u)}~.
  % \end{equation}
  \begin{equation}\label{eq:embed-loss}
    r \in \prop{\ell}(p) \iff \varphi(r) \in \prop{L}(p)~.
  \end{equation}
\end{definition}
%

@@

\begin{proposition}\label{prop:embed-bayes-risks}
  A loss $L$ embeds discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$.
  % A loss $L:\reals^d\to\reals^\Y$ embeds discrete $\ell:\R\to\reals^Y$ if and only if $\risk{L}=\risk{\ell}$.
\end{proposition}
\begin{proof}
  %\raft{$\impliedby$: First 2 sentences are good, but then it fogs up a bit.  3rd needs another careful pass, e.g., supporting hyperplane at what point?   4th cannot be right since you don't cover all reports $r$ \jessie{Took another pass}}
  \jessiet{Proof intuition in comment}
%	\jessie{Intuition: $\implies$: Take the injection given and take $\U = \varphi(\R)$.
%		Since we embed, the loss values match at these embedding points, and we know the surrogate has no ``strictly better'' report than the embedding, otherwise we would contradict the fact that $L$ embeds $\ell$, so the embedded report must be in the argmin of the surrogate restricted to $\U$, that is, $L|_\U$.  
%		At any $p \in \simplex$, suppose $r \in \argmin_{r'} \inprod{\ell(r)}{p}$.
%		As $\ell(r) = L(\varphi(r))$, we then have $\inprod{p}{\ell(r)} = \inprod{p}{L(\varphi(r))}$, and therefore we observe $\risk{L|_\U} = \risk{\ell}$ on $\simplex$.
%	The property $\gamma'$ elicited by $L|_\U$ is then nonempty for all $p \in \simplex$.
%	Moreover, we have $\risk{L} = \risk{L|_\U}$ by construction of $\gamma'$ and its nondegeneracy.
%	$\impliedby$: We know $\risk{\ell}$ is polyhedral, and classic results (Aurenhammer) show that the projection of the facets of the epigraph of $\risk{\ell}$ form a power diagram on the simplex.  Each cell of this power diagram corresponds to a level set of $\gamma_r$.  A corollary of each level set being a cell in a power diagram is that each $\gamma_r$ is full-dimensional.
%	We know there is a report $u_r$ such that $u_r \in \Gamma(\tilde p)$ for some $\tilde p \in \inter{\gamma_r}$.
%	Moreover, the point $(p, -\inprod{p}{L(u_r)})$ forms a supporting hyperplane of $-\risk{L}$ (and therefore $-\risk{\ell}$ as well) if and only if $u_r \in \Gamma(p)$ for $p \in \Gamma_{u_r}$. 
%	As $(p, -\inprod{p}{L(u_r)})$ also forms a supporting hyperplane of $-\risk{\ell}$, we must then have $p \in \gamma_r$.
%	As this is true for all $p \in \Gamma_{u_r}$, we must have $\Gamma_{u_r} = \gamma_r$.
%	Losses match by considering the supporting hyperplanes to the facets of the epigraphs of the Bayes Risks are the same, and the loss values are uniquely determined by the final coordinate by this final coordinate of the supporting hyperplane.}
  Throughout we have $L:\reals^d\to\reals^\Y_+$, $\ell:\R\to\reals^\Y_+$, and define $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
  Suppose $L$ embeds $\ell$ via the embedding $\varphi$.
%  Let $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
  Letting $\U := \varphi(\R)$, define $\gamma':\simplex \toto \U$ by $\gamma' : p \mapsto \Gamma(p)\cap \U$.
  To see that $\gamma'(p) \neq \emptyset$ for all $p\in\simplex$, note that by the definition of $\gamma$ as the property elicited by $\ell$ we have some $r \in \gamma(p)$, and by the embedding condition~\eqref{eq:embed-loss}, $\varphi(r) \in \Gamma(p)$.
  By Lemma~\ref{lem:loss-restrict}, we see that $L|_{\U}$ (the loss $L$ with reports restricted to $\U$) elicits $\gamma'$ and $\risk{L} = \risk{L|_{\U}}$.
  As $L(\varphi(\cdot)) = \ell(\cdot)$ by embedding condition (i), we have
  \begin{equation*}
    \risk{\ell}(p) = \min_{r \in \R}\inprod{p}{\ell(r)} = \min_{r \in \R}\inprod{p}{L(\varphi(r))} = \min_{u \in \U}\inprod{p}{L(u)} = \risk{L|_\U}(p) = \risk{L}(p)~,
  \end{equation*}
  for all $p\in\simplex$.

    \btw{RF: This is on the informal side, mostly because of the ``working in the affine hull'' bit.  It can all be formalized though, probably should be for the journal version: just take an appropriate linear projection of $\reals^n$ to $\reals^{n-1}$, and work with the projected versions of everything, and then project back.}
  For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
  In what follows, we implicitly work in the affine hull of $\simplex$ by taking an appropriate invertible linear projection to an affine subspace $A : \reals^n_+ \to \reals^{n-1}_+$, so that interiors are well-defined, and $\risk{\ell}$ may be differentiable on the interior of $\simplex$.
  (For intuition, one can consider the relative interiors in $\reals^n_+$, but we need to consider interiors in order to apply previous results.)
  Since $\ell$ is discrete, $-\risk{\ell}$ is polyhedral as the pointwise maximum of a finite set of linear functions.
%  Moreover, consider the linear transformation $P: \ell \mapsto [\mathbb{I}_{n-1}, \vec 0] \risk{\ell}$ projecting $\risk{\ell}$ down to $n-1$ dimensions.
  The projection of its epigraph $E_{\ell}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer}, whose cells are full-dimensional (in $n-1$ dimensions) and correspond to the level sets $\gamma_r$ of $\gamma = \prop{\ell}$. \jessiet{Don't need Theorem 1; can use Lemma~\ref{lem:finite-full-dim} instead.}

  For each $r\in\R$, let $p_r$ be a distribution in the interior of $\gamma_r$, and let $u_r \in \Gamma(p)$.
  Observe that, by definition of the Bayes risk and $\Gamma$, for all $v\in\reals^d$ the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports the epigraph $E_L$ of $-\risk{L}$ at the point $(p,-\inprod{p}{L(v)})$ if and only if $v\in\Gamma(p)$.
  Thus, the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports $E_L = E_\ell$ at the point $(p_r,-\inprod{p_r}{L(u_r)})$, and thus does so at the entire facet $\{(p,-\inprod{p}{L(u_r)}) : p\in\gamma_r\}$; by the above, $u_r \in \Gamma(p)$ for all such distributions as well.
  We conclude that $u_r \in \Gamma(p) \iff p \in \gamma_r \iff r \in \gamma(p)$, satisfying condition~\eqref{eq:embed-loss} for $\varphi : r \mapsto u_r$.
  To see that the loss values match, we merely note that the supporting hyperplanes to the facets of $E_L$ and $E_\ell$ are the same, and the loss values are uniquely determined by the supporting hyperplane.
  In particular, if $h$ supports the facet corresponding to $\gamma_r$, we have $\ell(r)_y = L(u_r)_y = h(\delta_y)$, where $\delta_y$ is the point distribution on outcome $y$.

@@

  A loss $L$ embeds a discrete loss if and only if $\risk{L}$ is polyhedral.

@@

  If $L$ embeds $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$, and its proof already argued that $\risk{\ell}$ is polyhedral since $\risk{\ell}$ is a pointwise max of a finite number of linear functions.

@@

  Defining $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$, the same proof shows that $L$ embeds $\ell$.

@@

	Now for $p \not \in \int{\simplex}$, consider $\Y'\subsetneq \Y$, $\Y'\neq\emptyset$.
	Applying the above argument, we have a similar guarantee: a finite set $\F_{\Y'}$ such that $\Gamma(p) \in \F_{\Y'}$ for all $p$ with support exactly $\Y'$.
	Taking $\F = \bigcup\{\F_{\Y'} | \Y'\subseteq\Y, \Y'\neq\emptyset\}$, we have for all $p\in\simplex$ that $\Gamma(p) \in \F$, giving $\U \subseteq \F$.
	As $\F$ is finite, so is $\U$, and the elements of $\U$ are closed polyhedra as faces of $D_{\Y'}$ for some $\Y'\subseteq\Y$.
\end{proof}

@@

\begin{theorem}\label{thm:poly-embeds-discrete}
  Every polyhedral loss $L$ embeds a discrete loss.
\end{theorem}
 \begin{proof}
 	\jessie{Lemma 4 is redundant with this proof, and we don't really need the proof.  We have $L$ polyhedral $\implies \risk{L}$ polyhedral (L4) $\iff$ $L$ embeds a discrete loss (P2).}
	The projection of the epigraph of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
	Defining the property $\gamma:\simplex\toto\R$ by $\gamma_r = C_r$ for $r\in\R$, we see that the same construction gives us points $u_r \in\reals^d$ such that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
	Define $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$.
	Since $L$ is polyhedral and $\gamma(p)\cap \R$ is nonempty for all $p \in \simplex$, we have $\risk{L} = \risk{L|_{\R}}$ polyhedral by Lemma~\ref{lem:poly-loss-poly-risk}.
 \end{proof}

@@

\begin{theorem}\label{thm:discrete-loss-poly-embeddable}
  Every discrete loss $\ell$ is embedded by a polyhedral loss.
\end{theorem}
\begin{proof}
  Let $n = |\Y|$, and let $C:\reals^n \to \reals$ be given by $(-\risk{\ell})^*$, the convex conjugate of $-\risk{\ell}$.
  From standard results in convex analysis, $C$ is polyhedral as $-\risk{\ell}$ is, and $C$ is finite on all of $\reals^\Y$ as the domain of $-\risk{\ell}$ is bounded~\cite[Corollary 13.3.1]{rockafellar1997convex}.
  Note that $-\risk{\ell}$ is a closed convex function, as the infimum of affine functions, and thus $(-\risk{\ell})^{**} = -\risk{\ell}$.
  Define $L:\reals^n\to\reals^\Y$ by $L(u) = C(u)\ones - u$, where $\ones\in\reals^\Y$ is the all-ones vector.
  We first show that $L$ embeds $\ell$, and then establish that the range of $L$ is in fact $\reals^\Y_+$, as desired.

@@

While Definition~\ref{def:loss-embed} gives the notion of one \emph{loss} embedding another, we now generalize the notion of one \emph{property} embedding another.
\begin{definition}\label{def:prop-embed}
	A property $\Gamma : \simplex \toto \reals^d$ embeds a property $\gamma:\simplex \toto \R$ if there exists some injective embedding $\varphi:\R \to \reals^d$ such that for all $p \in \simplex$ and $r \in \R$, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
	Moreover, we say a loss embeds a property when it embeds a loss eliciting the property.
\end{definition}

@@

\jessiet{New to journal version}
\begin{lemma}\label{lem:embed-defs-equiv}
	%  \raft{Introduce $L$}
	Let $L : \reals^d \to \reals^\Y_+$ be a loss function \proposedadd{whose infimum is attained in expectation for all $p \in \simplex$}.
	If the property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$, then there is a discrete loss $\ell$ such that $\ell$ elicits $\gamma$ and $L$ embeds $\ell$.
\end{lemma}
\begin{proof}
	\raft{All the important pieces are here, but take it slower.  State $\ell$ as a definition (let $\ell$ be given by...) and show why $L$ embeds it.\jessie{Took another pass but changed technique, adding in this detail.  Now very similar to the proof of Prop 1 forward direction.}}
	Consider a loss $\ell : \R \to \reals_+^\Y$, defined so that $\ell : r \mapsto L(\varphi(r))$, i.e. $\ell = L|_{\varphi(\R)}$, where $\varphi$ is the same embedding given by $\Gamma$ embedding $\gamma$.
	Now, we claim that $L$ embeds $\ell$, and by Proposition~\ref{prop:embed-bayes-risks}, we can simply show $\risk{L} = \risk{\ell}$.

>>>>

Several consistent convex surrogates in the literature can be thought of as ``embeddings'', wherein one maps the discrete reports to a vector space, and finds a convex loss which agrees with the original loss.
A key condition is that the original reports should be optimal exactly when the corresponding embedded points are optimal.
We formalize this notion as follows.
%
\begin{definition}[Embedding a loss]\label{def:loss-embed}
  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ if there exists some injective embedding $\varphi:\R\to\reals^d$ such that
  (i) for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\R$ we have
  % \begin{equation}\label{eq:embed-loss}
  %   r \in \argmin_{r'\in\R} \inprod{p}{\ell(r')} \iff \varphi(r) \in \argmin_{u\in\reals^d} \inprod{p}{L(u)}~.
  % \end{equation}
  \begin{equation}\label{eq:embed-loss}
    r \in \prop{\ell}(p) \iff \varphi(r) \in \prop{L}(p)~.
  \end{equation}
\end{definition}
\proposedadd{Moreover, we say $L$ embeds $\ell$ over the set $S$ if $L$ embeds $\ell|_S$ and $\prop{\ell}(p) \cap S \neq \emptyset$ for all $p\in \simplex$.}
%

@@

\begin{proposition}\label{prop:embed-bayes-risks}
  A loss $L:\reals^d \to \reals^\Y_+$ embeds discrete loss $\ell:\R \to \reals^\Y_+$ \proposedadd{for some set of reports $S \subseteq \R$} if and only if $\risk{L}=\risk{\ell}$.
  \jessie{This isn't quite right, since we really want $\risk{L} = \risk{\ell|_S}$; is this any set $S$ such that blah blah, by applying Lemma 1?}.  
  % A loss $L:\reals^d\to\reals^\Y$ embeds discrete $\ell:\R\to\reals^Y$ if and only if $\risk{L}=\risk{\ell}$.
\end{proposition}
\begin{proof}
  %\raft{$\impliedby$: First 2 sentences are good, but then it fogs up a bit.  3rd needs another careful pass, e.g., supporting hyperplane at what point?   4th cannot be right since you don't cover all reports $r$ \jessie{Took another pass}}
  \jessiet{Proof intuition in comment}
%	\jessie{Intuition: $\implies$: Take the injection given and take $\U = \varphi(\R)$.
%		Since we embed, the loss values match at these embedding points, and we know the surrogate has no ``strictly better'' report than the embedding, otherwise we would contradict the fact that $L$ embeds $\ell$, so the embedded report must be in the argmin of the surrogate restricted to $\U$, that is, $L|_\U$.  
%		At any $p \in \simplex$, suppose $r \in \argmin_{r'} \inprod{\ell(r)}{p}$.
%		As $\ell(r) = L(\varphi(r))$, we then have $\inprod{p}{\ell(r)} = \inprod{p}{L(\varphi(r))}$, and therefore we observe $\risk{L|_\U} = \risk{\ell}$ on $\simplex$.
%	The property $\gamma'$ elicited by $L|_\U$ is then nonempty for all $p \in \simplex$.
%	Moreover, we have $\risk{L} = \risk{L|_\U}$ by construction of $\gamma'$ and its nondegeneracy.
%	$\impliedby$: We know $\risk{\ell}$ is polyhedral, and classic results (Aurenhammer) show that the projection of the facets of the epigraph of $\risk{\ell}$ form a power diagram on the simplex.  Each cell of this power diagram corresponds to a level set of $\gamma_r$.  A corollary of each level set being a cell in a power diagram is that each $\gamma_r$ is full-dimensional.
%	We know there is a report $u_r$ such that $u_r \in \Gamma(\tilde p)$ for some $\tilde p \in \inter{\gamma_r}$.
%	Moreover, the point $(p, -\inprod{p}{L(u_r)})$ forms a supporting hyperplane of $-\risk{L}$ (and therefore $-\risk{\ell}$ as well) if and only if $u_r \in \Gamma(p)$ for $p \in \Gamma_{u_r}$. 
%	As $(p, -\inprod{p}{L(u_r)})$ also forms a supporting hyperplane of $-\risk{\ell}$, we must then have $p \in \gamma_r$.
%	As this is true for all $p \in \Gamma_{u_r}$, we must have $\Gamma_{u_r} = \gamma_r$.
%	Losses match by considering the supporting hyperplanes to the facets of the epigraphs of the Bayes Risks are the same, and the loss values are uniquely determined by the final coordinate by this final coordinate of the supporting hyperplane.}
  Throughout we have $L:\reals^d\to\reals^\Y_+$, $\ell:\R\to\reals^\Y_+$, and define $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
  Suppose $L$ embeds $\ell$ via the embedding $\varphi$.
%  Let $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
  Letting $\U := \varphi(\R)$, define $\gamma':\simplex \toto \U$ by $\gamma' : p \mapsto \Gamma(p)\cap \U$.
  To see that $\gamma'(p) \neq \emptyset$ for all $p\in\simplex$, note that by the definition of $\gamma$ as the property elicited by $\ell$ we have some $r \in \gamma(p)$, and by the embedding condition~\eqref{eq:embed-loss}, $\varphi(r) \in \Gamma(p)$.
  By Lemma~\ref{lem:loss-restrict}, we see that $L|_{\U}$ (the loss $L$ with reports restricted to $\U$) elicits $\gamma'$ and $\risk{L} = \risk{L|_{\U}}$.
  As $L(\varphi(\cdot)) = \ell(\cdot)$ by embedding condition (i), we have
  \begin{equation*}
    \risk{\ell}(p) = \min_{r \in \R}\inprod{p}{\ell(r)} = \min_{r \in \R}\inprod{p}{L(\varphi(r))} = \min_{u \in \U}\inprod{p}{L(u)} = \risk{L|_\U}(p) = \risk{L}(p)~,
  \end{equation*}
  for all $p\in\simplex$.

    \btw{RF: This is on the informal side, mostly because of the ``working in the affine hull'' bit.  It can all be formalized though, probably should be for the journal version: just take an appropriate linear projection of $\reals^n$ to $\reals^{n-1}$, and work with the projected versions of everything, and then project back.}
  For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
  In what follows, we implicitly work in the affine hull of $\simplex$ by taking an appropriate invertible linear projection to an affine subspace $A : \reals^n_+ \to \reals^{n-1}_+$, so that interiors are well-defined, and $\risk{\ell}$ may be differentiable on the interior of $\simplex$.
  (For intuition, one can consider the relative interiors in $\reals^\Y_+$, but we need to consider interiors in order to apply previous results.)
  Since $\ell$ is discrete, $-\risk{\ell}$ is polyhedral as the pointwise maximum of a finite set of linear functions.
%  Moreover, consider the linear transformation $P: \ell \mapsto [\mathbb{I}_{n-1}, \vec 0] \risk{\ell}$ projecting $\risk{\ell}$ down to $n-1$ dimensions.
  The projection of its epigraph $E_{\ell}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer}, whose cells are full-dimensional (in $n-1$ dimensions) and correspond to the level sets $\gamma_r$ of $\gamma = \prop{\ell}$. \jessiet{Don't need Theorem 1; can use Lemma~\ref{lem:finite-full-dim} instead. -21 Mar 21}

  \proposedadd{Take $S$ as follows: for each facet $F$ (of which there are finitely many) of the epigraph of $\ell$, $E_{\ell}$, there is at least one $r \in \R$ such that $(p, \inprod{p}{\ell(r)})$ supports $E_\ell$ on the facet $F$.
  Form $S$ by taking one such report for each facet.}
  For each $r\in\R\proposedadd{S}$, let $p_r$ be a distribution in the interior of $\gamma_r$, and let $u_r \in \Gamma(p)$.
  Observe that, by definition of the Bayes risk and $\Gamma$, for all $v\in\reals^d$ the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports the epigraph $E_L$ of $-\risk{L}$ at the point $(p,-\inprod{p}{L(v)})$ if and only if $v\in\Gamma(p)$.
  Thus, the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports $E_L = E_\ell$ at the point $(p_r,-\inprod{p_r}{L(u_r)})$, and thus does so at the entire facet $\{(p,-\inprod{p}{L(u_r)}) : p\in\gamma_r\}$; by the above, $u_r \in \Gamma(p)$ for all such distributions as well.
  We conclude that $u_r \in \Gamma(p) \iff p \in \gamma_r \iff r \in \gamma(p)$, satisfying condition~\eqref{eq:embed-loss} for $\varphi : r \mapsto u_r$.
  To see that the loss values match, we merely note that the supporting hyperplanes to the facets of $E_L$ and $E_\ell$ are the same, and the loss values are uniquely determined by the supporting hyperplane.
  In particular, if $h$ supports the facet corresponding to $\gamma_r$, we have $\ell(r)_y = L(u_r)_y = h(\delta_y)$, where $\delta_y$ is the point distribution on outcome $y$.

@@

  \proposedadd{There exists a set $S \subseteq \R$ such that the} loss $L$ embeds a discrete loss $\ell : \R \to \reals^\Y_+$ if and only if $\risk{L}$ is polyhedral.

@@

  If $L$ embeds $\ell$ \proposedadd{on a set $S$}, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$, and its proof already argued that $\risk{\ell}$ is polyhedral since $\risk{\ell}$ is a pointwise max of a finite number of linear functions.

@@

  Defining $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$, the same proof shows that $L$ embeds $\ell$ \proposedadd{on the set $\R$}.

@@

	Now for $p \not \in \inter{\simplex}$, consider $\Y'\subsetneq \Y$, $\Y'\neq\emptyset$.
	Applying the above argument, we have a similar guarantee: a finite set $\F_{\Y'}$ such that $\Gamma(p) \in \F_{\Y'}$ for all $p$ with support exactly $\Y'$.
	Taking $\F = \bigcup\{\F_{\Y'} | \Y'\subseteq\Y, \Y'\neq\emptyset\}$, we have for all $p\in\simplex$ that $\Gamma(p) \in \F$, giving $\U \subseteq \F$.
	As $\F$ is finite, so is $\U$, and the elements of $\U$ are closed polyhedra as faces of $D_{\Y'}$ for some $\Y'\subseteq\Y$.
\end{proof}

@@

\begin{theorem}\label{thm:poly-embeds-discrete}
  Every polyhedral loss $L$ embeds a discrete loss.
\end{theorem}
 \begin{proof}
 	\jessie{Why isn't this proof just:  We have $L$ polyhedral $\implies \risk{L}$ polyhedral (L4) $\iff$ $L$ embeds a discrete loss (P2).}
	The projection of the epigraph of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
	Defining the property $\gamma:\simplex\toto\R$ by $\gamma_r = C_r$ for $r\in\R$, we see that the same construction gives us points $u_r \in\reals^d$ such that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
	Define $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$.
	Since $L$ is polyhedral and $\gamma(p)\cap \R$ is nonempty for all $p \in \simplex$, we have $\risk{L} = \risk{L|_{\R}}$ polyhedral by Lemma~\ref{lem:poly-loss-poly-risk}.
 \end{proof}

@@

\begin{theorem}\label{thm:discrete-loss-poly-embeddable}
  For every discrete loss $\ell:\R \to \reals^\Y_+$ \proposedadd{there is a set $S \subseteq \R$ such that $\ell$} is embedded by a polyhedral loss \proposedadd{on $S$}.
\end{theorem}
\begin{proof}
  Let $n = |\Y|$, and let $C:\reals^n \to \reals$ be given by $(-\risk{\ell})^*$, the convex conjugate of $-\risk{\ell}$.
  From standard results in convex analysis, $C$ is polyhedral as $-\risk{\ell}$ is, and $C$ is finite on all of $\reals^\Y$ as the domain of $-\risk{\ell}$ is bounded~\cite[Corollary 13.3.1]{rockafellar1997convex}.
  Note that $-\risk{\ell}$ is a closed convex function, as the infimum of affine functions, and thus $(-\risk{\ell})^{**} = -\risk{\ell}$.
  Define $L:\reals^n\to\reals^\Y$ by $L(u) = C(u)\ones - u$, where $\ones\in\reals^\Y$ is the all-ones vector.
  We first show that $L$ embeds $\ell$, and then establish that the range of $L$ is in fact $\reals^\Y_+$, as desired.

@@

While Definition~\ref{def:loss-embed} gives the notion of one \emph{loss} embedding another, we now generalize the notion of one \emph{property} embedding another.
\begin{definition}\label{def:prop-embed}
	A property $\Gamma : \simplex \toto \reals^d$ embeds a property $\gamma:\simplex \toto \R$ \proposedadd{for a set $S \subseteq \R$ such that $\gamma(p) \cap S \neq \emptyset$ for all $p \in \simplex$} if there exists some injective embedding $\varphi:\R \to \reals^d$ such that for all $p \in \simplex$ and $r \in \R$, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
	Moreover, we say a loss embeds a property when it embeds a loss eliciting the property.
\end{definition}

@@

\jessiet{New to journal version}
\begin{lemma}\label{lem:embed-defs-equiv}
	%  \raft{Introduce $L$}
	Let $L : \reals^d \to \reals^\Y_+$ be a loss function \proposedadd{whose infimum is attained in expectation for all $p \in \simplex$}.
	If the property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$ \proposedadd{on $S$}, then there is a discrete loss $\ell:\R \to \reals^\Y_+$ such that $\ell$ elicits $\gamma$ and $L$ embeds $\ell$ \proposedadd{on $S$}.
\end{lemma}
\begin{proof}
	\raft{All the important pieces are here, but take it slower.  State $\ell$ as a definition (let $\ell$ be given by...) and show why $L$ embeds it.\jessie{Took another pass but changed technique, adding in this detail.  Now very similar to the proof of Prop 1 forward direction.}}
	Consider a loss $\ell : \R \to \reals_+^\Y$, defined so that $\ell : r \mapsto L(\varphi(r))$, i.e. $\ell = L|_{\varphi(\R)}$, where $\varphi$ is the same embedding given by $\Gamma$ embedding $\gamma$.
	Now, we claim that $L$ embeds $\ell$ \proposedadd{on the set $S$}, and by Proposition~\ref{prop:embed-bayes-risks}, we can simply show $\risk{L} = \risk{\ell}$.
